Psychological Needs During Intergroup Contact: Three Experience Sampling Studies

### 2022-10-26 Methods-and-Results.Rmd
path models render init

View(mdlTblGeneralLmAll)

@@

@@

>>>>

@@

shortMdlPath <- list()
for(i in 1:length(mdlPrep)){
  study <- gsub("S", "Study", str_extract(mdlPrep[[i]]$fit$data, "S1|S2|S3"))
  dv <- gsub("Raw", "", sub(" ~.*", "", mdlPrep[[i]]$fit$formula)) 
  pred <- gsub("\\(Intercept\\)", "", paste(mdlPrep[[i]]$coeficients$coef, collapse = ''))

  name <- paste(study, dv, pred, sep='.')
  shortMdlPath[[name]] <- mdlPrep[[i]]$coeficients[, c("coef", "est", "Bstar", "B", "estBeta", "BetaStar", "Beta")]
}

@@

```{r Export Path Models}
save(shortMdlPath, 
     file = "data/theoryMdlTabl.RData")
```

### 2022-10-26 Methods-and-Results.tex
path models render init

Thus, almost all other extracted topics fall into broader or narrower
need concepts that are commonly discussed within the psychological needs
literature. Something about need theories/models plus our own review
article.

>>>>

Thus, almost all other extracted topics fall into broader or narrower
need concepts that are commonly discussed within the psychological needs
literature \citep[e.g.,][]{Orehek2018a} and offer insight into a core
aspect of the migration experience that has remained broadly
under-explored \citep[][]{Kreienkamp2022d}.

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{save}\NormalTok{(shortMdlPath, }
     \AttributeTok{file =} \StringTok{"data/theoryMdlTabl.RData"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}
